---
output:
  xaringan::moon_reader:
    seal: false
    lib_dir: libs
    css: [default, fonts.css, animate.css]
    nature:
      slideNumberFormat: |
        <div class="progress-bar-container">
          <div class="progress-bar" style="width: calc(%current% / %total% * 100%);">
          </div>
        </div>
      ratio: '16:9'
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(icon)
library(emo)
```

class: center, middle
# Introduction

???

As we've established earlier in the course, most quantitative research studies focus on statistical inference. That's the process where you have some observed data from a sample of a population and you use it to build an underlying model to draw conclusions about the population. Probability is the study of how data can be generated from a model. This serves as the foundation for statistical inference. Understanding this will enable you to better appraise the quality of evidence from quantiative research studies. 

Let's begin by looking at one of the simplest process for generating random data - the coin flip. By exploring coin flipping, you'll learn the basic laws and methods of probability. 

---

class: top, left
# Flipping a coin to generate a random variable
--
```{r include=FALSE}
set.seed(4)
```
```{r}
rbinom(1, 1, 0.5)
```
--

```{r}
rbinom(1, 1, 0.5)
```


???

Each time I flip a fair coin, it has a fifty percent chance of being heads and a 50% chance of being tales. In statistical terms, we could describe it as a random variable. We can call one case of simulating from this random variable - a draw. If you don't have a coin handy, we can use the computer to simulate this random event. Specifically, we can use a function rbinom. This is names because it's generates any number of random draws that you would like from a binomial distribution. We're going to learn about the binomial distribution in a moment. To generate the random variable using rbinom, we input three arguments - first is the number of random draws we want to generate - in other words this is how many coin tosses we want to simulate - the second argument is the number of coins to flip on each draw - in this situation is just one. The third argument is the probability of the coin toss being heads, which for a fair coin is fifty percent. There are two possible outcomes - zero or 1. In this case we got a result of one We could interpret the result of one as heads. The pound signs followed by 1 in square brackets just signals the output from the program - we can completely ignore it. 

This is a random process, which means if we run the same lines of code again, we might get the same or a difference result. In this case, we get a zero - we interpret this as tails. 

---

class: top, left
# Flipping multiple coins
--
```{r}
rbinom(10, 1, 0.5)
```
--
```{r}
rbinom(10, 1, 0.5)
```


???

It doesn't make much sense to run the same calculatation multiple times just to simulate single coin tosses. Instead, we just change the first argument in the rbinom function. For example, here we simulate 10 coin tosses all at once. In this case the results were five ones or heads and five zeros or tails. Let's run that again. This time we got seven ones. Each time we do a set of flips, we'll see a different set of outcomes. Right now each draw has only one coin flip. 

---

class: top, left
# Flipping multiple coins

```{r}
rbinom(1, 10, 0.5)
```
--
```{r}
rbinom(10, 10, 0.5)
```

???

A different approach would be to use the second argument to specify how many coins should be flipped within each. If we set it to ten coins, then the result will simply be the number heads out of ten. Or we could say that we want to do multiple draws of multiple coins. In this case, we're saying we want to flip ten coins ten times. This shows us that when we flip ten coins, the resulting number of heads might three, six, five or so on. Notice that the most common result was five. That will be relevant later. 
---

class: top, left
# Unfair coins
--
```{r}
rbinom(10, 10, 0.8)
```
--
```{r}
rbinom(10, 10, 0.2)
```

???
Until now we've been talking about a coin that has a fifty percent chance of coming up heads. Not all random events have an equal likelihood of happening. We could extend the coin analogy and call such circumstances biased coins. These would be coins more likely to turn up heads than tails or vice versa. We can control this probability by changing the third argument in the function. When the third argument is point eight, that means each flip has an eighty percent chance of resulting in heads. When we flip one of these unfair coins te times, we notice that the most common result is around seven to nine heads out of ten. When the third argument is point 2, each row of draws has around one to three heads. 
---

class: top, left
# Binomial distribution

## Binomial(*size,p*),

where size is the number of flips and p is the probability that each is heads. 

???

We can consider this process of flipping a number of biased coins and calculating the resulting number of heads as a random variable that follows a binomial distribution. We can describe a binomial distribution by two characteristics. These are the size, which in our example is the number of coin flips, and p, which is the probability that each flip is heads. Further on we're going to learn to reason about this distribution as a foundation for learning about statistical inference. 


---

class: center, middle
# Up next

???
Time now to have a quick bit of fun and generate a binomial distribution "flipping" some coins yourself. 





