---
output:
  xaringan::moon_reader:
    seal: false
    lib_dir: libs
    css: [default, fonts.css, animate.css]
    nature:
      highlightStyle: github
      highlightLines: true
      ratio: '16:9'
    includes:
      in_header: fa.html
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(icon)
library(emo)
library(tidyverse)
library(ggplot2)
set.seed(3)
```

class: center, middle, hide-count
# How accurate is our estimate of the mean?


???

Let's revisit the last exercises where we looked into a hypothetical example of a sample of scores about the levels of burnout from six nurses. We were able to calculate that the sample mean was one hundred and six. However, we know that this mean is only an estimate of the true population mean burnout score in the whole population of nurses, which is the value that we are really interested in. It is unlikely that we would ever be able to know the average value of burnout from the whole population though so we have to rely on estimates from smaller samples as the best approximation that we can get.
---

class: middle, center, hide-count

# Not all samples are created equal


???

What we have to keep in mind though, is that not all samples are created equal. Some are better estimates than others. Generally speaking, larger samples will provide better estimates of the mean of the population. But how can we quantify the accuracy of the estimate of a mean taken from a sample, given its size?

---

class: top, left, hide-count

# Creating a sampling distribution

--


- Drew a sample of 50 nurses and asked them to rate their *leadership capability* on a scale from 0 - 15
- Mean score in this sample was 9.7 with a standard deviation of 2.1

---

class: top, left, hide-count

# Creating a sampling distribution

- Drew a sample of 50 nurses and asked them to rate their *leadership capability* on a scale from 0 - 15
- Mean score in this sample was 9.7 with a standard deviation of 2.1


```{r fig.show="animate", animation.hook = 'gifski', fig.width=7, fig.height=3, echo=FALSE, message=FALSE, warning=FALSE, results = 'hide', interval=0.08, loop=FALSE, cache=TRUE}
library(ggplot2)
library(tweenr)
library(parallel)
library(MASS)
ppplot <- function(sub){
x <- round(rnorm(50, 9.7, 2.1))
m <- mean(x)
df <- data.frame(x = x, y = 23)
dfs <- list(df)
for(i in seq_len(nrow(df))) {
  dftemp <- tail(dfs, 1)
  dftemp[[1]]$y[i] <- sum(dftemp[[1]]$x[seq_len(i)] == dftemp[[1]]$x[i])
  dfs <- append(dfs, dftemp)
}
dfs <- append(dfs, dfs[rep(length(dfs), 3)])
dft <- tween_states(dfs, 10, 1, 'cubic-in', 50)
dft$y <- dft$y - 0.5
dft <- dft[dft$y != 23, ]
ppl <- function(frame){
  p <- ggplot(data=dft[dft$.frame==frame,],aes(x=x, y=y))+geom_point(shape=16, color="green3", size=4)+ylim(0,16)+xlim(3,17)+theme_light()+theme(panel.border=element_blank(), panel.grid.minor=element_blank())+labs(x="Leadership score", y=NULL)
  df <- data.frame()
  p2 <- ggplot(df) + geom_point() + xlim(0, 16) + ylim(3, 17)+theme_void()
  p3 <- ggplot(df) + geom_point() + xlim(8.7, 10.7) + ylim(0, 150)+theme_light()+theme(panel.border=element_blank(), panel.grid.minor=element_blank())+labs(x="Sample means", y=NULL)
  cowplot::plot_grid(p,p2,p3, align="h",rel_widths = c(1,0.55, 1), ncol = 3)
  
}
ppl2 <- function(frame){
  p <- ggplot(data=dft[dft$.frame==53,],aes(x=x, y=y))+geom_point(shape=16, color="green3", size=4)+ylim(0,16)+xlim(3,17)+theme_light()+theme(panel.border=element_blank(), panel.grid.minor=element_blank())+geom_vline(xintercept = m, linetype=2)+labs(x="Leadership score", y=NULL)
  p
  df <- data.frame()
  lb1 <- paste0("mean", "[", sub, "]", " == ", round(m,2))
  p2 <- ggplot(df) + geom_point() + xlim(0, 16) + ylim(3, 17)+theme_void()+annotate("text", x = 8, y=10, label=lb1, parse = TRUE, size=7)+annotate("segment", x = 1, xend = 15, y = 8, yend = 8, colour = "black", size=1, arrow=arrow(type = "closed", length = unit(0.3,"cm")))
  p3 <- ggplot(df) + geom_point() + xlim(8.7, 10.7) + ylim(0, 150)+theme_light()+theme(panel.border=element_blank(), panel.grid.minor=element_blank())+annotate("segment", x = m, xend = m, y = 20, yend = 4, colour = "black", size=1, arrow=arrow(type = "closed", length = unit(0.3,"cm")))+labs(x="Sample means", y=NULL)
  cowplot::plot_grid(p,p2,p3, align="h", rel_widths = c(1,0.55,1), ncol = 3)
}
pf <- list(lapply(seq(1,53,2),function(x) ppl(x)), lapply(rep(53,3), function(x) ppl(x)), lapply(1:40, function(x) ppl2()))
return(pf)
}
mclapply(1:3, function(x) ppplot(x), mc.cores = 8, mc.cleanup = TRUE)
circleFun <- function(center=c(0,0), diameter=1, npoints=100, start=0, end=2, filled=TRUE){
  tt <- seq(start*pi, end*pi, length.out=npoints)
  df <- data.frame(
    x = center[1] + diameter / 2 * cos(tt),
    y = center[2] + diameter / 2 * sin(tt)
  )
  if(filled==TRUE) { 
    df <- rbind(df, center)
  }
  return(df)
}
fullCircle <- circleFun(c(1, -1), 2.3, start=0, end=2, filled=FALSE)
fullCircle2 <- circleFun(c(1, -1), 2, start=0, end=2, filled=FALSE)
fullCircle3 <- circleFun(c(1, -1), 1.3, start=0, end=2, filled=FALSE)
fullCircle4 <- circleFun(c(1, -1), 0.3, start=0, end=2, filled=FALSE)
fullCircle5 <- circleFun(c(1, -1), 0.1, start=0, end=2, filled=FALSE)
tris <- circleFun(c(1, -1), 1.6, start=1.2, end=-0.2, filled=FALSE, npoints=50)
tris2 <- circleFun(c(1, -1), 0.2, start=1.4, end=0, filled=FALSE, npoints=50)
tris3 <- circleFun(c(1, -1), 0.2, start=1, end=-0.4, filled=FALSE,npoints=50)
s <- c(rep(1,10), 1:50)
trii <- lapply(s, function(x) data.frame(x=c(tris[x,1],tris2[x,1],tris3[x,1]), y=c(tris[x,2],tris2[x,2],tris3[x,2])))
quarterCircle <- circleFun(c(1,-1), diameter = 1.85, start=1, end=1.25, filled=TRUE)
quarterCircle2 <- circleFun(c(1,-1), diameter = 1.85, start=0.75, end=1, filled=TRUE)
quarterCircle3 <- circleFun(c(1,-1), diameter = 1.85, start=0.5, end=0.75, filled=TRUE)
quarterCircle4 <- circleFun(c(1,-1), diameter = 1.85, start=0.25, end=0.5, filled=TRUE)
quarterCircle5 <- circleFun(c(1,-1), diameter = 1.85, start=0.25, end=0, filled=TRUE)
quarterCircle6 <- circleFun(c(1,-1), diameter = 1.85, start=2, end=1.75, filled=TRUE)
x <- round(rnorm(50, 9.7, 2.1))
m <- mean(x)
df <- data.frame(x = x, y = 23)
dfs <- list(df)
for(i in seq_len(nrow(df))) {
  dftemp <- tail(dfs, 1)
  dftemp[[1]]$y[i] <- sum(dftemp[[1]]$x[seq_len(i)] == dftemp[[1]]$x[i])
  dfs <- append(dfs, dftemp)
}
dfs <- append(dfs, dfs[rep(length(dfs), 3)])
dft <- tween_states(dfs, 10, 1, 'cubic-in', 50)
dft$y <- dft$y - 0.5
dft <- dft[dft$y != 23, ]
dft <- dft[dft$.frame %in% c(1:26, seq(27, 53, 2)),]
dft$.frame <- rep(1:40, each=50)
plots <- function(dd){
p <- ggplot() + 
  geom_polygon(data=fullCircle, aes(x, y), color="#40596b", fill="#40596b") +
  geom_polygon(data=fullCircle2, aes(x, y), color="white", fill="white") +
  geom_polygon(data=quarterCircle, aes(x,y), color="#cdd6e0", fill="#cdd6e0") + 
  geom_polygon(data=quarterCircle2, aes(x,y), color="#acb3ba", fill="#acb3ba") + 
  geom_polygon(data=quarterCircle3, aes(x,y), color="#ffd15c", fill="#ffd15c") +
  geom_polygon(data=quarterCircle4, aes(x,y), color="#f8b64c", fill="#f8b64c") +
  geom_polygon(data=quarterCircle5, aes(x,y), color="#ff7058", fill="#ff7058") +
  geom_polygon(data=quarterCircle6, aes(x,y), color="#f1543f", fill="#f1543f") +
  geom_polygon(data=fullCircle3, aes(x,y), color="white", fill="white") +
  geom_polygon(data=fullCircle4, aes(x,y), color="#40596b", fill="#40596b") +
  geom_polygon(data=trii[[dd]], aes(x,y), color="#40596b", fill="#40596b") +
  geom_polygon(data=fullCircle5, aes(x,y), color="white", fill="white") +
  coord_equal() +
  theme_void()
  ddd <- ifelse(dd<20, 1, ifelse(dd<35, 2, ifelse(dd<45, 3, ifelse(dd<50, 4, ifelse(dd<53, 5, ifelse(dd<55, 6, ifelse(dd<57, 7, ifelse(dd<59, 8, base::sample(1:10,1)))))))))
  p2 <- ggplot(data=dft[dft$.frame==dd,],aes(x=x, y=y))+geom_point(shape=16, color="green3", size=4)+ylim(0,16)+xlim(3,17)+theme_light()+theme(panel.border=element_blank(), panel.grid.minor=element_blank())+labs(x="Leadership score", y=NULL)
  df <- data.frame()
  p3 <- ggplot(df) + geom_point() + xlim(8.7, 10.7) + ylim(0, 150)+theme_light()+theme(panel.border=element_blank(), panel.grid.minor=element_blank())+labs(x="Sample means", y=NULL)
  cowplot::plot_grid(p2,p,p3, align="h",rel_widths = c(1,0.55, 1), ncol=3)
}
lapply(seq(1,40,3), function(x) plots(x))
hists <- function(x){
  x <- round(rnorm(50, 9.7, 2.1))
  m <- mean(x)
  return(m)
}  
dh <- do.call(rbind, lapply(1:1000, function(x) hists()))
 hh <- function(x){
  d <- data.frame(Height=dh[1:x])
  return(d)
}
dhh <<- lapply(1:1000, function(x) hh(x))
plots2 <- function(dd){
p <- ggplot() + 
  geom_polygon(data=fullCircle, aes(x, y), color="#40596b", fill="#40596b") +
  geom_polygon(data=fullCircle2, aes(x, y), color="white", fill="white") +
  geom_polygon(data=quarterCircle, aes(x,y), color="#cdd6e0", fill="#cdd6e0") + 
  geom_polygon(data=quarterCircle2, aes(x,y), color="#acb3ba", fill="#acb3ba") + 
  geom_polygon(data=quarterCircle3, aes(x,y), color="#ffd15c", fill="#ffd15c") +
  geom_polygon(data=quarterCircle4, aes(x,y), color="#f8b64c", fill="#f8b64c") +
  geom_polygon(data=quarterCircle5, aes(x,y), color="#ff7058", fill="#ff7058") +
  geom_polygon(data=quarterCircle6, aes(x,y), color="#f1543f", fill="#f1543f") +
  geom_polygon(data=fullCircle3, aes(x,y), color="white", fill="white") +
  geom_polygon(data=fullCircle4, aes(x,y), color="#40596b", fill="#40596b") +
  geom_polygon(data=trii[[dd]], aes(x,y), color="#40596b", fill="#40596b") +
  geom_polygon(data=fullCircle5, aes(x,y), color="white", fill="white") +
  coord_equal() +
  theme_void()
  ddd <- ifelse(dd<20, 1, ifelse(dd<35, 2, ifelse(dd<45, 3, ifelse(dd<50, 4, ifelse(dd<53, 5, ifelse(dd<55, 6, ifelse(dd<57, 7, ifelse(dd<59, 8, base::sample(1:10,1)))))))))
  set.seed(ddd)
  x <- round(rnorm(50, 9.7, 2.1))
m <- mean(x)
df <- data.frame(x = x, y = 23)
dfs <- list(df)
for(i in seq_len(nrow(df))) {
  dftemp <- tail(dfs, 1)
  dftemp[[1]]$y[i] <- sum(dftemp[[1]]$x[seq_len(i)] == dftemp[[1]]$x[i])
  dfs <- append(dfs, dftemp)
}
dfs <- append(dfs, dfs[rep(length(dfs), 3)])
dft <- tween_states(dfs, 10, 1, 'cubic-in', 50)
dft$y <- dft$y - 0.5
dft <- dft[dft$y != 23, ]
  p2 <- ggplot(data=dft[dft$.frame==53,],aes(x=x, y=y))+geom_point(shape=16, color="green3", size=4)+ylim(0,16)+xlim(3,17)+theme_light()+theme(panel.border=element_blank(), panel.grid.minor=element_blank())+geom_vline(xintercept = m, linetype=2)+labs(x="Leadership score", y=NULL)
  df <- data.frame()
p3 <- ggplot(data = dhh[[dd-40]], aes(x = Height)) +
  geom_histogram(binwidth = 0.1, color = "white", fill="green3") +
  theme_light() +
  scale_y_continuous(limits = c(0,150)) +
  labs(x=NULL, y=NULL) +
  xlim(8.7, 10.7) + 
  theme(panel.border=element_blank(), panel.grid.minor=element_blank()) +
  labs(x="Sample means", y=NULL)
  cowplot::plot_grid(p2,p,p3, align="h",rel_widths = c(1,0.55, 1), ncol=3)
}
lapply(seq(41,50,2), function(x) plots2(x))
lapply(seq(51,60,1), function(x) plots2(x))
plots3 <- function(dd){
  
p <- ggplot() + 
  geom_polygon(data=fullCircle, aes(x, y), color="#40596b", fill="#40596b") +
  geom_polygon(data=fullCircle2, aes(x, y), color="white", fill="white") +
  geom_polygon(data=quarterCircle, aes(x,y), color="#cdd6e0", fill="#cdd6e0") + 
  geom_polygon(data=quarterCircle2, aes(x,y), color="#acb3ba", fill="#acb3ba") + 
  geom_polygon(data=quarterCircle3, aes(x,y), color="#ffd15c", fill="#ffd15c") +
  geom_polygon(data=quarterCircle4, aes(x,y), color="#f8b64c", fill="#f8b64c") +
  geom_polygon(data=quarterCircle5, aes(x,y), color="#ff7058", fill="#ff7058") +
  geom_polygon(data=quarterCircle6, aes(x,y), color="#f1543f", fill="#f1543f") +
  geom_polygon(data=fullCircle3, aes(x,y), color="white", fill="white") +
  geom_polygon(data=fullCircle4, aes(x,y), color="#40596b", fill="#40596b") +
  geom_polygon(data=trii[[60]], aes(x,y), color="#40596b", fill="#40596b") +
  geom_polygon(data=fullCircle5, aes(x,y), color="white", fill="white") +
  coord_equal() +
  theme_void()
x <- round(rnorm(50, 9.7, 2.1))
m <- mean(x)
df <- data.frame(x = x, y = 23)
dfs <- list(df)
for(i in seq_len(nrow(df))) {
  dftemp <- tail(dfs, 1)
  dftemp[[1]]$y[i] <- sum(dftemp[[1]]$x[seq_len(i)] == dftemp[[1]]$x[i])
  dfs <- append(dfs, dftemp)
}
dfs <- append(dfs, dfs[rep(length(dfs), 3)])
dft <- tween_states(dfs, 10, 1, 'cubic-in', 50)
dft$y <- dft$y - 0.5
dft <- dft[dft$y != 23, ]
  p2 <- ggplot(data=dft[dft$.frame==53,],aes(x=x, y=y))+geom_point(shape=16, color="green3", size=4)+ylim(0,16)+xlim(3,17)+theme_light()+theme(panel.border=element_blank(), panel.grid.minor=element_blank())+geom_vline(xintercept = m, linetype=2)+labs(x="Leadership score", y=NULL)
  
hh <- function(x){
  d <- data.frame(Height=dh[1:x])
  return(d)
}
dhh <- lapply(1:1000, function(x) hh(x))
p3 <- ggplot(data = dhh[[dd+40]], aes(x = Height)) +
  geom_histogram(binwidth = 0.1, color = "white", fill="green3") +
  theme_light() +
  scale_y_continuous(limits = c(0,150)) +
  labs(x=NULL, y=NULL) +
  xlim(8.7, 10.7) + 
  theme(panel.border=element_blank(), panel.grid.minor=element_blank()) +
  labs(x="Sample means", y=NULL)
  cowplot::plot_grid(p2,p,p3, align="h",rel_widths = c(1,0.55, 1), ncol = 3)
}
mclapply(seq(1,300, 20), function(x) plots3(x), mc.cores = 8, mc.cleanup = TRUE)
plots3.2 <- function(dd){
sub <- dd+40  
x <- round(rnorm(50, 9.7, 2.1))
m <- mean(x)
df <- data.frame(x = x, y = 23)
dfs <- list(df)
for(i in seq_len(nrow(df))) {
  dftemp <- tail(dfs, 1)
  dftemp[[1]]$y[i] <- sum(dftemp[[1]]$x[seq_len(i)] == dftemp[[1]]$x[i])
  dfs <- append(dfs, dftemp)
}
dfs <- append(dfs, dfs[rep(length(dfs), 3)])
dft <- tween_states(dfs, 10, 1, 'cubic-in', 50)
dft$y <- dft$y - 0.5
dft <- dft[dft$y != 23, ]
df <- data.frame()
  lb1 <- paste0("mean", "[", sub, "]", " == ", round(m,1))
  p <- ggplot(df) + geom_point() + xlim(0, 16) + ylim(3, 17)+theme_void()+annotate("text", x = 1, y=10, label=lb1, parse = TRUE, size=7,hjust = 0)+annotate("segment", x = 1, xend = 15, y = 8, yend = 8, colour = "black", size=1, arrow=arrow(type = "closed", length = unit(0.3,"cm")))
  p2 <- ggplot(data=dft[dft$.frame==53,],aes(x=x, y=y))+geom_point(shape=16, color="green3", size=4)+ylim(0,16)+xlim(3,17)+theme_light()+theme(panel.border=element_blank(), panel.grid.minor=element_blank())+geom_vline(xintercept = m, linetype=2)+labs(x="Leadership score", y=NULL)
  
hh <- function(x){
  d <- data.frame(Height=dh[1:x])
  return(d)
}
dhh <- lapply(1:1000, function(x) hh(x))
p3 <- ggplot(data = dhh[[dd+40]], aes(x = Height)) +
  geom_histogram(binwidth = 0.1, color = "white", fill="green3") +
  theme_light() +
  scale_y_continuous(limits = c(0,150)) +
  labs(x=NULL, y=NULL) +
  xlim(8.7, 10.7) + 
  theme(panel.border=element_blank(), panel.grid.minor=element_blank()) +
  labs(x="Sample means", y=NULL)
  cowplot::plot_grid(p2,p,p3, align="h",rel_widths = c(1,0.55, 1), ncol = 3)
}
mclapply(seq(301,960, 20), function(x) plots3.2(x), mc.cores = 8, mc.cleanup = TRUE)
x <- round(mvrnorm(50, 9.8, 2.1^2, empirical = T))
m <- mean(x)
df <- data.frame(x = x, y = 23)
dfs <- list(df)
for(i in seq_len(nrow(df))) {
  dftemp <- tail(dfs, 1)
  dftemp[[1]]$y[i] <- sum(dftemp[[1]]$x[seq_len(i)] == dftemp[[1]]$x[i])
  dfs <- append(dfs, dftemp)
}
dfs <- append(dfs, dfs[rep(length(dfs), 3)])
dft <- tween_states(dfs, 10, 1, 'cubic-in', 50)
dft$y <- dft$y - 0.5
dft <- dft[dft$y != 23, ]
plots4 <- function(dd){
  
df <- data.frame()
  lb1 <- paste0("mean", "[", 1000, "]", " == ", 9.8)
  p <- ggplot(df) + geom_point() + xlim(0, 16) + ylim(3, 17)+theme_void()+annotate("text", x = 1, y=10, label=lb1, parse = TRUE, size=7,hjust = 0)+annotate("segment", x = 1, xend = 15, y = 8, yend = 8, colour = "black", size=1, arrow=arrow(type = "closed", length = unit(0.3,"cm")))
  p2 <- ggplot(data=dft[dft$.frame==53,],aes(x=x, y=y))+geom_point(shape=16, color="green3", size=4)+ylim(0,16)+xlim(3,17)+theme_light()+theme(panel.border=element_blank(), panel.grid.minor=element_blank())+geom_vline(xintercept = 9.8, linetype=2)+labs(x="Leadership score", y=NULL)
  
hh <- function(x){
  d <- data.frame(Height=dh[1:x])
  return(d)
}
dhh <<- lapply(1:1000, function(x) hh(x))
p3 <- ggplot(data = dhh[[dd+40]], aes(x = Height)) +
  geom_histogram(binwidth = 0.1, color = "white", fill="green3") +
  theme_light() +
  scale_y_continuous(limits = c(0,150)) +
  labs(x=NULL, y=NULL) +
  xlim(8.7, 10.7) + 
  theme(panel.border=element_blank(), panel.grid.minor=element_blank()) +
  labs(x="Sample means", y=NULL)
  cowplot::plot_grid(p2,p,p3, align="h",rel_widths = c(1,0.55, 1), ncol = 3)
}
mclapply(rep(960, 40), function(x) plots4(x), mc.cores = 8, mc.cleanup = TRUE)
```

???

One way is to use simulations to generate data not just from a single sample but from many, many samples of the same size. Let's look at a different example now. Say we were interested in measuring the leadership capabilities of registered nurses. to do this, we drew a sample of fifty nurses and asked them to rate their confidence in leadership skills on an instrument that ranges from zero to fifteen. The mean score was nine point seven and the standard deviation was two point one in our sample.

In a moment, I'm going to show an animation that will illustrate the process of creating a distribution using information from our sample by randomly simulating one thousand other samples of the same size. This is called a sampling distribution. Each random sample will consist of fifty scores, and we'll create one thousand samples in total. 

In the histogram on the left, each dot signifies one of the fifty scores from a random sample. After each sample histogram is completed, the mean is calculated. The mean of the first random sample is nine point two. This mean value is then subsequently added to the histogram of the sampling distribution on the right. As you can see, this process is repeated, allowing the sampling distribution on the right to build up. Looking at the spread of mean leadership values on the right, we can get a sense of the range of many possible estimates of the population mean that a sample of fifty nurses can produce. Notice that the range of possible mean values were between eight point nine and ten point seven. This means that mean values outside of this range are essentially improbable based on the information we gained from the 50 nurses in our sample. 
---
class: top, left, hide-count

# Sample size and sampling distribution

```{r, echo=FALSE, message= FALSE, warning=FALSE, cache = TRUE}
library(ggplot2)
samp <- function(n){
  x <- rnorm(n, 9.7, 2.1)
  m <- mean(x)
  s <- sd(x)
  return(c(m,s))
}
d <- as.data.frame(do.call(rbind, lapply(1:1000, function(x) samp(5))))
d2 <- as.data.frame(do.call(rbind, lapply(1:1000, function(x) samp(50))))
d3<- as.data.frame(do.call(rbind, lapply(1:1000, function(x) samp(500))))
colnames(d) <- colnames(d2) <- colnames(d3) <- c("mean", "sd")
p <- ggplot(data = d, aes(x = mean)) +
  geom_histogram(binwidth = 0.06, color = "white", fill="green3") +
  theme_light() +
  scale_y_continuous(expand = c(0,0)) +
  labs(x="Sample means N=5", y=NULL) +
  theme(panel.border=element_blank(), panel.grid.minor=element_blank(), legend.position = , legend.background = ) +
  xlim(6.7,12.7) 
p2 <- ggplot(data = dhh[[1000]], aes(x = Height)) +
  geom_histogram(binwidth = 0.06, color = "white", fill="green3") +
  theme_light() +
  scale_y_continuous(expand = c(0,0)) +
  labs(x="Sample means N=50", y="Frequency") +
  theme(panel.border=element_blank(), panel.grid.minor=element_blank(), legend.position = , legend.background = ) +
  xlim(6.7,12.7)
p3 <- ggplot(data = d3, aes(x = mean)) +
  geom_histogram(binwidth = 0.06, color = "white", fill="green3") +
  theme_light() +
  scale_y_continuous(expand = c(0,0)) +
  labs(x="Sample means N=500", y=NULL) +
  theme(panel.border=element_blank(), panel.grid.minor=element_blank(), legend.position = , legend.background = ) +
  xlim(6.7,12.7)
cowplot::plot_grid(p3,p2,p, ncol = 1, align = "hv") 
```

???

To demonstrate the point that larger samples provide better estimates of the target population, we can explore what happens if we redo this sampling experiment, but this time sampling five hundred nurses instead of fifty, before taking the mean each time, and repeating this until one thousand sample mean values have been recorded. For completeness, let’s also do the same with samples of just five nurses each. We compare the resulting sampling distributions from all three scenarios here, with the plot in the middle corresponding to the sampling distribution we already generated in the previous animation. What do we notice? Well, for one thing, all the histograms look like a normal distribution with that characteristic bell curve shape. But we can also quite easily notice that the distributions generated from the smaller samples down the bottom are more dispersed or spread out than the one with 500 nurses in each sample up the top.

---
class: center, middle, hide-count

# Let's practice

???

In the next exercise - it's your turn to create some sampling distributions to test the relationship between sampling distribution and sample size. 


