---
output:
  xaringan::moon_reader:
    seal: false
    lib_dir: libs
    css: [default, fonts.css, animate.css]
    nature:
      slideNumberFormat: |
        <div class="progress-bar-container">
          <div class="progress-bar" style="width: calc(%current% / %total% * 100%);">
          </div>
        </div>
      ratio: '16:9'
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(icon)
library(emo)
library(tidyverse)
knitr::opts_chunk$set( fig.height=5) 
set.seed(3)
```

class: center, middle
# Introduction

???
When you flip a fair coin ten times, what do you think is the most likely number of heads? Well, since heads and tails are equally likely, you can probably figure out that the most likely outcome is that five come up heads and five come up tails. Say I offer you a bet - if it is exactly that result, I'll pay you a dollar, otherwise, you'll pay me a dollar. Should you take the bet?
---

class: top, left
# Simulating many outcomes

X ~ Binomial(10,5)

Pr(X = 5)

???
To answer that question, we have to find the probability of binomial random variable x, with those parameters, ten flips each with a fifty percent probability resulting in an outcome of five. We could express this as Pr, short for probability, x equals five. 
---

class: top, left
# Simulating many outcomes

```{r}
flips <- rbinom(100000,10,0.5)
```
--

```{r echo=FALSE}
suppressMessages(library(ggplot2))
options(warn=-1)
ggplot2::qplot(flips, geom="histogram", binwidth = 0.5, ylab = "count")+
  theme_minimal()
```

???
One way to find out if you should take the bet, is to simulate many different draws - say a hundred thousand and then see how common each outcome is. As we saw in the last exercises, we can choose the number of draws by setting the first argument of rbinom. The resulting variable, which we have named flips, then contains the result of these one hundred thousand draws. To figure out what's going on, we can plot the results using a histogram. Each bar shows the relative frequency of one outcome - the different possible outcomes are zero heads out of ten flips all the way up to ten heads out of ten flips. Histograms are a common way to examine probability distributions. Notice that out of these hundred thousand draws, about twenty five thousand are equal to five. 
---

class: top, left
## Density

```{r echo=FALSE}
set.seed(3)
```
```{r}
mean(flips == 5)
```
```{r echo=FALSE}
suppressMessages(library(ggplot2))
options(warn=-1)
tibble::tibble(flips) %>% 
  mutate(Bet = ifelse(flips==5, "Chances you win", "Chances you lose")) %>% 
ggplot2::ggplot(aes(flips))+
  geom_histogram(aes(fill=Bet), binwidth = 0.5)+
  theme_minimal()
```

???
A next step on our way to figuring out if you should take my bet or not, is to calculate the fraction of outcomes that were equal to five. It turns out that out of the one hundred thousand draws, twenty four point six percent of the time there were five heads out of the ten flips. In other words there is a twenty four point six percent chance of you winning the bet. Another way to term this fraction we have calculatate is it is the density of the distribution at point five. 
---

class: top, left
# Cumulative density

Pr(X <= 4)
```{r}
mean(flips <= 4)
```
--
```{r echo=FALSE}
tibble::tibble(flips) %>% 
  mutate(Bet = ifelse(flips<=4, "Chances you win", "Chances you lose")) %>% 
ggplot2::ggplot(aes(flips))+
  geom_histogram(aes(fill=Bet), binwidth = 0.5)+
  theme_minimal()
```


???

So now you know not to take my bet. More likely than not, we won't get exactly five heads out of ten. What if I offer a new bet, I'll pay you a dollar if four or fewer come up heads, otherwise you have to pay me. This describes the cumulative density of the distribution. Insted of calculating the fraction of times that five heads came up out of ten, we calculate the fraction of times that four or less heads came up out of ten. In this case, there was about a thirty eight percent chance that you would win. Or in other words, you still probably shouldn't take my bet.  

---

class: center, middle
# Up next

???

Let's put your understanding of the binomial probability distribution to the test in the next exercises.  



