---
output:
  xaringan::moon_reader:
    seal: false
    lib_dir: libs
    css: [default, fonts.css, animate.css]
    nature:
      slideNumberFormat: |
        <div class="progress-bar-container">
          <div class="progress-bar" style="width: calc(%current% / %total% * 100%);">
          </div>
        </div>
      ratio: '16:9'
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(icon)
library(emo)
library(tidyverse)
library(ggplot2)
knitr::opts_chunk$set( fig.height=5) 
set.seed(3)
```

class: center, middle
# Introduction

???
So far we've been exploring the binomial distribution with the example of flipping a coin and counting the number of heads. Now we're going to introduce another important probability distribution. You'll see how the principles you've learned about working with random variables and simulation are important far beyond the binomial. 
---
class: top, left
# Flipping 10 coins

```{r}
flips <- rbinom(10000,10,0.5)
```

```{r echo=FALSE}
suppressMessages(library(ggplot2))
options(warn=-1)
tibble::tibble(flips) %>% 
  mutate(Bet = ifelse(flips<=4, "Chances you win", "Chances you lose")) %>% 
ggplot2::ggplot(aes(flips))+
  geom_histogram(binwidth = 0.5)
```

???

So far we've often looked at binomial consisting of 10 flips of a coin that has a fifty percent chance of heads. That would look like this distribution - a histogram where the most common value is five. 

---
class: top, left
# Flipping 10 coins

```{r}
flips <- rbinom(10000,1000,0.5)
```

```{r echo=FALSE}
suppressMessages(library(ggplot2))
options(warn=-1)
tibble::tibble(flips) %>% 
  mutate(Bet = ifelse(flips<=4, "Chances you win", "Chances you lose")) %>% 
ggplot2::ggplot(aes(flips))+
  geom_histogram(aes(y=..density..), colour=alpha("gray", 0.4), fill = alpha("gray", 0.4), binwidth = 4)+
 geom_density(color = alpha("#FF6666", 0), alpha = 0.2, fill="#FF6666")+
  theme_minimal()+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank())+ geom_hline(yintercept=0, colour="white", size=1)
```

???

Now instead imagine that we've flipped one thousand coins ten thousand times. Now the distribution of heads is centered around 500. Notice the distribution is now taking on a sort of symmetrical bell curve shape. This is because when you draw from a binomial with a very large size, that is, many coin flips, the result approximates a normal distribution. This normal distribution is famous because many distributions in nature take this shape, included measurement errors in scientific experiments. Most of the common statisical analysis methods you'll come across in quantitative nursing research studies are based on the normal distribution. 

---
class: top, left
# Normal distribution has mean and standard deviation

```{r echo=FALSE}
suppressMessages(library(ggplot2))
options(warn=-1)
tibble::tibble(flips) %>% 
  mutate(Bet = ifelse(flips<=4, "Chances you win", "Chances you lose")) %>% 
ggplot2::ggplot(aes(flips))+
  geom_histogram(aes(y=..density..), colour=alpha("gray", 0.4), fill = alpha("gray", 0.4), binwidth = 4)+
 geom_density(color = alpha("#FF6666", 0), alpha = 0.2, fill="#FF6666")+
  theme_minimal()+
  theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank())+ geom_hline(yintercept=0, colour="white", size=1)+
  geom_vline(xintercept=500,linetype="dashed", color = "gray", size = 1)+
  annotate("text", colour = "white", size = 12, x = 500, y = 0.010, label = "mean")+
  annotate("text", colour = "white", size = 12, x = 510, y = 0.005, label = "sd")
```

???

While the binomial is determined by the parameters size and p, that is the number of flips and their probability of heads, the normal is defined by two other parameters, the mean and standard deviation. The standard deviation 


